---
title: "Milestone Report"
author: "David"
date: "31/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE, warning=FALSE)
```

## Load the tidyverse and tidytext packages
First of all, we will load key libraries for our analysis.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(tidytext)
library(dplyr)
library(ggplot2)
library(DT)
data(stop_words)
```

## Summary

We will read the files in the "en_US" folder and convert them into the tidy text format.

```{r cache=FALSE}
file_list <- list.files(pattern = "*en_US*",
                        recursive = TRUE)

texts <- data.frame(file=character(),
                    paragraph=as.numeric(),
                    text=character(),
                    stringsAsFactors = FALSE) # creates empty dataframe

for (i in 1:length(file_list)) {
  p <- read.delim(file_list[i],
                  header=FALSE,
                  col.names = "text",
                  stringsAsFactors = FALSE) # read.delim here is automatically splitting by paragraph
  p <- p %>% mutate(file=sub(".txt", "", x=file_list[i]), # add filename as label
                    paragraph=row_number()) # add paragraph number
  texts <- bind_rows(texts, p) # adds to existing dataframe
}
words <- texts %>% unnest_tokens(word, text)
head(words)
```

Now we will remove stop words like "a", "after", "you" or "your". 

```{r}
words <- words %>% anti_join(stop_words)
```

After we have removed stop words, we will display a datatable with the number of times each words appears in the texts.

```{r}
words_count <- words %>% count(word,sort = TRUE)
words_count %>% head(1000) %>% datatable()
```

Here we have a histogram with the top 10 words by their number of times each word appears.

```{r}
words_count %>% 
  head() %>% 
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_col() +
  labs(y = NULL)
```



